Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-11-25 manuscript.Rmd
demographic information

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(rgdal)

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(sf)
library(rgdal)

@@

demographic_data <- read.csv("DC_demographic_data.csv", header = FALSE)
names <- unlist(demographic_data[2,])
demographic_data <- demographic_data %>% 
  slice(3:8096)
head(demographic_data)
colnames(demographic_data) <- names
head(demographic_data)
